**Measuring Depression and Anxiety with 4 items? Adaptation of the PHQ-4 to increase its Sensitivity to Subclinical Variability**

### 2024-12-14 paper/4_WIP/manuscript.qmd
fix numbers to match the figure results
@AnafNeves can you update the preprint

The results suggested that in the subclinical range of the BDI-II, the correlation between its score and the PHQ-4 Depression score was marginally higher (although not significantly, $p_{one-sided} = 0.161$) for the refined version compared to the original one. No correlation differences were observed in the moderate to severe range of the BDI-II.

For the STAI-5, there was no difference in the correlation between the refined and the original version in the subclinical range of the STAI-5. Surprisingly, we observed a stronger correlation between the refined PHQ-4 Anxiety score and the STAI-5 in the moderate to severe range compared to the original version ($p_{one-sided} = 0.027$).

>>>>

The results suggested that in the subclinical range of the BDI-II, the correlation between its score and the PHQ-4 Depression score was marginally higher (although not significantly, $p_{one-sided} = 0.164$) for the refined version compared to the original one. No correlation differences were observed in the moderate to severe range of the BDI-II.

For the STAI-5, there was no difference in the correlation between the refined and the original version in the subclinical range of the STAI-5. Surprisingly, we observed a stronger correlation between the refined PHQ-4 Anxiety score and the STAI-5 in the moderate to severe range compared to the original version ($p_{one-sided} = 0.017$).
